---
title: "PS 811 W7"
author: "Mingcong Pan"
date: "2021/12/1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create the following graphs in `ggplot2`.

### 1. Check out the base R built-in dataset, `data("USArrests")`.

```{r echo=FALSE, warning = FALSE, message = FALSE, results = "asis"}
library(ggplot2)
USArrests <- cbind(rownames(USArrests), USArrests)

```

### 2. Create a scatterplot that looks at the correlation between murder and assault arrests. Label the x and y axes and title the graph.

```{r echo=FALSE, warning = FALSE, message = FALSE, results = "asis"}
ggplot(USArrests, aes(x=Murder, y=Assault)) + 
  geom_point() +  ggtitle("Scatter plot: correlation between murder and assault arrests") + 
  xlab("Murder") + ylab("Assault")
```

### 3. Create a boxplot of rape arrests. Label the plot.

```{r echo=FALSE, warning = FALSE, message = FALSE, results = "asis"}
ggplot(USArrests, aes(x="", y =Rape)) + 
  geom_boxplot() +  ggtitle("Box plot: Rape") + 
  xlab("Rape")
  
```

### 4. Create a barplot of the number of rape arrests per state.

```{r echo=FALSE, warning = FALSE, message = FALSE, results = "asis"}
ggplot(USArrests, aes(x=rownames(USArrests), y=Rape)) + 
  geom_bar(stat = "identity") + scale_x_discrete(guide = guide_axis(n.dodge=6)) + 
  ggtitle("Barplot: number of rape arrests per state") + 
  xlab("State") + ylab("Rape")

```

### 5. Create a histogram for the percent of urban population.

```{r echo=FALSE, warning = FALSE, message = FALSE, results = "asis"}
ggplot(USArrests, aes(x=UrbanPop)) + geom_histogram() + 
  ggtitle("Histogram: the percent of urban population") + 
  xlab("Percentage of urban population") + ylab("Count")

```
